### 2018-03-22 latex/sc18/plots.tex
starting to put together plots

% macros for plotting
\newcommand{\datafile}{}
\newcommand{\run}{}
\newcommand{\numiterations}{30}
\newcommand{\minvalue}{1}

@@

% set options for relative error over time plot
\newcommand{\relerrplotoptions}{
	xlabel=Time (s),
	\ifylabel
		ylabel=Relative Error,
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=1.8in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

% plot relative error over time, filtering rows out appropriately
\newcommand{\relerrplot}{
\begin{axis}[\relerrplotoptions]
	\addplot+ [discard if not={algo}{liavas},discard if not={runs}{\run},green,thick,mark options={solid}] table [x={totaltime}, y={relerr}] {\datafile};
	\addplot+ [discard if not={algo}{nodimtree},discard if not={runs}{\run},red,thick,mark options={solid},mark=square*] table [x={totaltime}, y={relerr}] {\datafile};
	\addplot+ [discard if not={algo}{dimtree},discard if not={runs}{\run},blue,thick,mark options={solid},mark=triangle*] table [x={totaltime}, y={relerr}] {\datafile};
	\iflegend
		\legend{Liavas, Classic, DimTree}
	\fi
\end{axis}
}

\newcommand{\strongscalingplot}{
\begin{axis}[\relerrplotoptions]
	\addplot+ [discard if not={algo}{liavas},discard if not={runs}{\run},green,thick,mark options={solid}] table [x={nodes}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={algo}{nodimtree},discard if not={runs}{\run},red,thick,mark options={solid},mark=square*] table [x={nodes}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={algo}{dimtree},discard if not={runs}{\run},blue,thick,mark options={solid},mark=triangle*] table [x={nodes}, y={totaltime}] {\datafile};
	\iflegend
		\legend{Liavas, Classic, DimTree}
	\fi
\end{axis}
}

>>>>

% macros for plotting
\newcommand{\datafile}{}
\newcommand{\alg}{}
%\newcommand{\numiterations}{30}
%\newcommand{\minvalue}{1}

@@

% set options for strongscaling plot
\newcommand{\strongscalingplotoptions}{
	xlabel=Time (s),
	\ifylabel
		ylabel=Relative Error,
		ylabel style={yshift=-.3cm},
	\fi
	\ifwider
		width=1.8in, height=2in,
	\else
		width=1.35in, height=2in,
	\fi
	y tick label style={
        /pgf/number format/.cd,
            precision=4,
	},
	legend style={draw=none, cells={align=left}, nodes={scale=0.7}}
}

% plot time over p, filtering rows out appropriately
\newcommand{\strongscalingplot}{
\begin{axis}[\strongscalingplotoptions]
	%\addplot+ [discard if not={algo}{liavas},thick,mark options={solid}] table [x={nodes}, y={totaltime}] {\datafile};
	%\addplot+ [discard if not={algo}{nodimtree},thick,mark options={solid},mark=square*] table [x={nodes}, y={totaltime}] {\datafile};
	\addplot+ [discard if not={alg}{D},thick,mark options={solid},mark=triangle*] table [x={p}, y={total_d}] {\datafile};
	\iflegend
		\legend{Liavas, Classic, DimTree}
	\fi
\end{axis}
}
